\textbf{Analyzing Machupo virus-receptor binding by molecular dynamics simulations}

### 2014-01-05 paper.tex
Claus's edits.

The computational prediction of mutational effects on protein--protein interactions remains a challenging problem. Several methods are available to perform an energy difference calculation from an experimentally determined co-crystal structure. For example, end point methods can be performed rapidly, with relatively low computational cost \citep{Grant2011,Kortemme2004}. However, such methods can suffer from various simplifying assumptions. For example, they generally use an implicit solvent approximation and assume the end state difference with minimal structural rearrangement is sufficient to discriminate energetic differences \citep{Grant2011,Kortemme2004}. Alternative approaches have been developed using machine learning, training coefficients in a weighted equation containing geometric and energetic parameters \citep{Vreven2011,Vreven2012,Bajaj2011,Hwang2010}. Unfortunately, such machine-learning approaches often suffer in novel applications, for which available training sets are small or non-existent. As such, these methods are poorly suited for most host-virus protein--protein systems. By contrast, first principles methods can forgo training, but currently available methods such as free energy perturbation (FEP) and thermodynamic integration (TI) rely on a transitional model (where one state may be wild-type and the other may be a mutant) to make rigorous free energy calculations  \citep{Gilson1997,Lu2004,Chodera2011,Gumbart2013}. While these may be considered two of the gold standard techniques for calculating affinity differences, there are a huge number theoretical and technical complexities that must all be properly managed to ensure a converged solution \citep{Gumbart2013b}. Such considerations quickly come to dominate the protocol, and the necessary book keeping introduces the possibility of human error \citep{Gumbart2013b}. Moreover, as the two ending states look ever more dissimilar the chances of convergence falls rapidly. To ensure convergence, these techniques are typically limited to small differences (such as point mutant comparisons) with a few, very impressive exceptions \citep{Wang2006,Gumbart2013,Gumbart2013b}. For most, larger differences quickly become intractable as the number of intermediate steps required to compute a converged solution grows or the complexity of adding restraining potentials and computing approximations expands \citep{Wang2006,Gumbart2013,Gumbart2013b}.

Here we propose applying an existing method to a new test case to probe mutational effects in protein--protein interactions based on first principles simulation. We impart a pulling force within an all-atom molecular dynamics simulation on one member of the complex while the other is held in place. Then, we measure the force required for dissociation \citep{Gumbart2012,Lu1999,Park2004,Is2001A,Is2001B}. As a proxy for relative binding affinity, we use the maximum applied force required for separation and the area under the force-versus-distance curve (AUC). Although such biasing techniques are common in protein-ligand binding problems, they are less commonly applied to protein--protein interactions, and almost never to mutational analysis in a protein--protein system. This is largely the result of free energy convergence difficulties and computational limitations \citep{Cuendet2008,Cuendet2011}; using maximum force or simple AUC can solve these problems. We also used the traditional dual topology FEP technique to compute relative free energy differences for comparison to our simplified force biased approach.

@@

For our experiments, we used the experimentally determined GP1/hTfR1 structure (PDBID: 3KAS) \citep{Abraham2010}. The apical domain of hTfR1 interacts directly with GP1 while the other two domains are closer to the cell membrane and have essentially no interaction with GP1. The biophysical independence of the apical domain allowed us to isolate it without significantly affecting the GP1/hTfR1 interaction.

@@

The exact NAMD configuration file is made available as a supplement and a github repository with all necessary set up files is provided. We used the Charmm27 \citep{Brooks1983} all-atom force field. The initial system temperature was set to 310K. Several typical MD settings were used including switching and cutoff distances (see provided configuration file). In addition, we used a 2 femtosecond time step with rigid bonds. We used periodic boundary conditions with the particle mesh ewald (PME) method of computing full system electrostatics outside of the explicit box. Furthermore, we used a group pressure cell, flexible box, langevin barostat and lavegin thermostat during equilibration. A harmonic restraint (called harmonic constraint in VMD) was set as stated previously.

To start the simulation, the barostat was switched off and the system was minimized for 1000 steps. Next, the fixed backbone was released, and the system was minimized for an additional 1000 time steps. Subsequently, the system was released into all-atom molecular dynamics for 3000 steps. Finally, the langevin piston was turned on and the system was simulated for 2 ns (1,000,000 steps) of chemical time. For each mutant, twenty independent equilibration replicates were run with an identical protocol.

@@

We used the final state from each equilibrated system to restart another MD simulation. Our steering protocol is fundamentally similar to \citet{Cuendet2008} with slightly different parameter choices. Perhaps the one significant difference lies in our choosing to not use a thermostat or barostat. However, this should not be a problem since we are not trying to calculate the binding free energy by any physically rigorous approach (the Jarzynski inequality being one example). Following equilibration, the final state of each simulation was used to generate a configuration file fixing the $\alpha$-carbon on residues 1, 58, 73-83, 96, 136, 137, 138, and 161 (again with linear numbering) in the hTfR1. These residues were selected as they are far from the binding interface and sufficiently distributed to prevent any orientational motion of the receptor relative to the viral spike protein. The center of mass of the $\alpha$-carbons of all residues (163-318 in linear numbering) in GP1 received an applied force during the simulation. The NAMD convention does not actually apply a force to all $\alpha$-carbon atoms, but rather uses the selection to compute an initial center of mass. Then, during the steering run, the single center of mass point is pulled with the parameters desribed below. We used the same force field parameters (exclude, cutoff, switching, etc.), the same integrator parameters (time step, rigidbonds on, all molecular being wrapped, etc.), and the same particle mesh ewald parameters as in equilibration. Periodic boundary conditions were incorporated as part of the system (as is the convention in NAMD restart) and PME was again used to approximate full system electrostatics.

We ran test simulations at several force constants, and visually inspected the results. A force constant of 5~kcal/mol/\AA$^2$ was chosen due to its relatively low signal-to-noise ratio. This is slightly lower than the more common 7~kcal/mol/\AA$^2$ found in several recent studies; however, it seems that value is so commonly selected primarily because it is the force constant found in the NAMD, SMD tutorial available through the developers. Moreover, the force constant could very likely be set to a range of nearby values with little loss in predictive power. In SMD experiments the pulling velocity should be as low as possible for the available computational time \citet{Cuendet2008,Cuendet2011}. Thus we choose a velocity of 0.000001~\AA/fs = 1~\AA/ns, and direction down the positive $z$-axis. This number could be set to pull faster if the computing time must be reduced, but slower than necessary pulling speeds are not typically considered problematic.

@@

Again, the NAMD configuration file is made available as a supplemental file. We used a similar configuration to that in equilibration. One significant difference was to make a cubic water box with a side length equal to the long axis of the complex plus a 10~\AA\  buffer on either side, and simply restrict center of mass motion with the NAMD setting. This was done to avoid affecting the system energy while calculating free energy differences.

@@

The FEP analysis tool in VMD was used for subsequent analysis. We used it to perform error analysis and compute the Bennett acceptance ratio as the maximum likelihood free energy difference of the two states under consideration. Though the larger transitions presented difficulty in a small number of windows, forward and reverse hysteresis was generally in good agreement for all complexes. The double mutants were performed by first doing the Y211A mutation followed by the other of the two mutants. Then, the numbers were simply added together to get the total energetic difference.

@@

\subsection{The GP1/hTfR1 system}
The GP1/hTfR1 interface marks a particularly important and useful test system. There are several sites on both the human and viral protein known to affect the infectivity phenotype of MACV. Many of the important sites have been mapped by \textit{in vitro} flow-cytometry based entry assays. The GP1/hTfR1 interface appears not to be dominated by one particular type of interaction (electrostatics, hydrogen-bonding, or van der Waals). In addition, much of the binding domain on hTfR1 is on a loop that is flexible prior to viral binding, but organizes to become a strand of a $\beta$-sheet on binding. As a result,  many other computational techniques \citep{Grant2011,Kortemme2004} only marginally useful. The complex nature of this interface represents a particularly difficult challenge for traditional computational analysis.

In total, we tested 7 point mutants and 3 double mutants in addition to the WT complex (Table~\ref{tab:summary_mutants} and Figure~\ref{fig:mutant_comparison}). All of the mutations are within 5~\AA\ of the protein--protein interface. Mutations at site hTfR1 site 211 have proven capable of causing loss-of-entry according to \textit{in vitro} flow-cytometry infection assays or known host-range limitations \citep{Rad2008,Rad20111,Rad20112}. Most likely, this effect is caused by the destruction of a critical hydrogen bond to Ser113 or Ser111 in GP1. The lost hydrogen bond would lead to the subsequent loss of a large hydrogen-bonding network seen in the crystal structure (Table~\ref{tab:summary_mutants}) \citep{Abraham2010}. In a manner similar to site 211, Asn348 appears to be important for binding by participating in a critical hydrogen bonding network \citep{Rad2008,Abraham2010} to GP1. In particular, Asn348Lys is reported in the literature to cause significantly reduced viral entry \textit{in vivo} (Table~\ref{tab:summary_mutants}) \citep{Rad2008,Abraham2010}. Finally, an alanine mutation at site 111 in GP1 (mutation vArg111Ala) has also been shown to cause decreased entry (Table~\ref{tab:summary_mutants}) \citep{Rad20112}. For notation purposes, the viral site is always referred to with a preceding `v'.

Despite, the fact that viral binding occurs at the site of a flexible loop in the free hTfR structure, our data shows after binding the strand is extremely rigid. All two sites had receptor strand have root mean squared fluctuation (RMSF) values in the top half of all receptor sites during equilibration (Figure~\ref{fig:rmsf}), and those are almost completely exposed to solvent. This is unsurprising considering the high degree of burial that occurs as a result of viral binding. Computing the root mean squared deviation (RMSD) of the entire structure over the trajectory shows that none of the mutations are so deleterious as the cause rapid unbinding. In fact, the RMSD over trajectory looks incredibly invariant across mutants (Figure~\ref{fig:rmsd}). By comparison to the equilibration RMSF calculation, near the end of the SMD trajectory all of the residues in the WT receptor interfacial strand are in the top half of RMSF over all receptor sites (Figure~\ref{fig:rmsf_comparison}). Thus, if sufficient simulation time is not dedicated to allowing this unfolding process, standard free energy techniques may miss the energetic contributions that result from ordering the flexible loop in the hTfR apical domain.

@@

We proceeded to compare our SMD results to that of the standard dual topology FEP approach to calculate relative free energy differences. The correlation between the energetically rigorous FEP and our statistical approach is high. For all 11 complexes tested, the correlation between max force and FEP was r=-0.767 at p=0.005857 (Figure~\ref{fig:fep}), and the correlation between AUC and FEP was r=--0.729 at p=0.011. As a result of the strong correlation, we will generally refer to the SMD differences only.

@@

We would like to emphasize here that we cannot expect perfect agreement between our simulations and the available experimental data, but the correspondence to a well established free energy method is bolsters our conclusions. While we have shown that our method can distinguish individual point mutations, we do not know the limit of detection with our method. First, it is possible that some mutants display measurable phenotypic effects in experiments yet appear identical in simulation. More extensive sampling or refinement of the simulation protocol could help to differentiate such mutants (see also next paragraph). Second, the SMD method is fundamentally limited by the accuracy of our starting structure. Third, the available experimental data for the GP1/hTfR1 system were generally obtained from entry assays or whole-cell binding assays rather than molecular binding assays. A mutant may cause a phenotypic difference in infectivity without generating a signal by our method. For example, entry could be lost in the experimental system because the protein is grossly or partially misfolded. An additional analytical step with circular dichroism or an analogous technique could clarify such large-scale folding differences. Further, since our simulations start with a bound structure, any changes that may dramatically affect the rate of association (different folds, trafficking issues, etc.) or relative orientation of the two proteins would be underestimated by our method.

@@

More importantly, with no \textit{a priori} knowledge of the appropriate number of equilibration samples, the during of equilibration, the appropriate number of pulling runs, or the best pulling speed means the computational expense in our SMD protocol may not be commensurate with the information provided. For example, another all atom approach that makes calculations via short simulations of spatially restrained complexes has proven capable of generating relatively accurate binding affinities with less compute time than is required from our steering strategy \citep{Gumbart2013,Gumbart2013b}. That being said, there is no reason to believe this SMD approach to mutagenic studies could not be optimized to reduce computational expense. Further analysis would be needed to understand the lower limits of resources required for accurate predictions.

@@

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/rmsfs.pdf}}
\caption{\label{fig:rmsf}\title{RMSF values during equilibration.} The RMSF values for every site in the bound complex computed during the equilibration phase of the protocol. Each color represents the average over 20 trajectories of a single mutant. Indices 17-25 are the hTfR flexible loop. The plot shows the flexibility of each site is essentially independent of mutation, and two sites above 0.72~\AA\ are found on the receptor in the interface.}
\end{figure}

@@

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/fep_mutants.pdf}}
\caption{\label{fig:fep}\title{Max force versus free energy perturbation} Scatter plot of maximum force in SMD versus the relative free energy difference calculated by FEP for all 10 mutants tested plus the WT complex. The WT complex for FEP was simply set to 0.0. The correlation between the two is r=-0.767 with p=0.005857.}
\end{figure}

>>>>

The computational prediction of mutational effects on protein--protein interactions remains a challenging problem. Several methods are available to perform an energy difference calculation from an experimentally determined co-crystal structure. For example, end point methods can be performed rapidly, with relatively low computational cost \citep{Grant2011,Kortemme2004}. However, such methods can suffer from various simplifying assumptions. For example, they generally use an implicit solvent approximation and assume the end state difference with minimal structural rearrangement is sufficient to discriminate energetic differences \citep{Grant2011,Kortemme2004}. Alternative approaches have been developed using machine learning, training coefficients in a weighted equation containing geometric and energetic parameters \citep{Vreven2011,Vreven2012,Bajaj2011,Hwang2010}. Unfortunately, such machine-learning approaches often suffer in novel applications, for which available training sets are small or non-existent. As such, these methods are poorly suited for most host-virus protein--protein systems. By contrast, first principles methods can forgo training, but currently available methods such as free energy perturbation (FEP) and thermodynamic integration (TI) rely on a transitional model (where one state may be wild-type and the other may be a mutant) to make rigorous free energy calculations  \citep{Gilson1997,Lu2004,Chodera2011,Gumbart2013}. While these may be considered two of the gold standard techniques for calculating affinity differences, there are a huge number of theoretical and technical complexities that must all be properly managed to ensure a converged solution \citep{Gumbart2013b}. Such considerations quickly come to dominate the protocol, and the necessary book keeping introduces the possibility of human error \citep{Gumbart2013b}. Moreover, as the two ending states look ever more dissimilar the chances of convergence fall rapidly. To ensure convergence, these techniques are typically limited to small differences (such as point mutant comparisons) with a few, very impressive exceptions \citep{Wang2006,Gumbart2013,Gumbart2013b}. For most investigators, larger differences quickly become intractable as the number of intermediate steps required to compute a converged solution grows or the complexity of adding restraining potentials and computing approximations expands \citep{Wang2006,Gumbart2013,Gumbart2013b}.

Here we propose that much of these complexities can be avoided if all we are interested in is a relative comparison of the effects of different mutations on protein-protein interactions, rather than measuring an absolute or relative binding affinity with experimentally realistic units. We impart a pulling force within an all-atom molecular dynamics simulation on one member of the complex while the other is held in place. Then, we measure the force required for dissociation \citep{Gumbart2012,Lu1999,Park2004,Is2001A,Is2001B}. As a proxy for relative binding affinity, we use the maximum applied force required for separation and the area under the force-versus-distance curve (AUC). Although such biasing techniques are commonly used in protein-ligand binding problems, they are less commonly applied to protein--protein interactions, and almost never to mutational analysis in a protein--protein system. This is largely the result of free energy convergence difficulties and computational limitations \citep{Cuendet2008,Cuendet2011}; using maximum force or simple AUC can solve these problems. For comparison, we also calculate relative free energy differences using the traditional dual topology FEP paradigm, and we show that the two approaches yield congruent results.

@@

For our experiments, we used the experimentally determined GP1/hTfR1 structure (PDB-ID: 3KAS) \citep{Abraham2010}. The apical domain of hTfR1 interacts directly with GP1 while the other two domains are closer to the cell membrane and have essentially no interaction with GP1. The biophysical independence of the apical domain allowed us to isolate it without significantly affecting the GP1/hTfR1 interaction.

@@

The exact NAMD configuration file is made available as a github repository with all necessary set up files is provided. We used the Charmm27 \citep{Brooks1983} all-atom force field. The initial system temperature was set to 310K. Several typical MD settings were used including switching and cutoff distances (see provided configuration files). In addition, we used a 2 femtosecond time step with rigid bonds. We used periodic boundary conditions with the particle mesh ewald (PME) method of computing full system electrostatics outside of the explicit box. Furthermore, we used a group pressure cell, flexible box, langevin barostat, and lavegin thermostat during equilibration. A harmonic restraint (called harmonic constraint in VMD) was set as stated previously.

To start the simulation, the barostat was switched off and the system was minimized for 1000 steps. Next, the fixed backbone was released, and the system was minimized for an additional 1000 time steps. Subsequently, the system was released into all-atom molecular dynamics for 3000 steps. Finally, the langevin barostat was turned on and the system was simulated for 2 ns (1,000,000 steps) of chemical time. For each mutant, twenty independent equilibration replicates were run with an identical protocol.

@@

We used the final state from each equilibrated system to restart another MD simulation. Our steering protocol is fundamentally similar to \citet{Cuendet2008} with slightly different parameter choices. Perhaps the one significant difference lies in our choosing to not use a thermostat or barostat. We can make this choice because we are not trying to calculate the binding free energy by any physically rigorous approach (the Jarzynski inequality being one example). Following equilibration, the final state of each simulation was used to generate a configuration file fixing the $\alpha$-carbon on residues 1, 58, 73-83, 96, 136, 137, 138, and 161 (again with linear numbering) in the hTfR1. These residues were selected as they are far from the binding interface and sufficiently distributed to prevent any orientational motion of the receptor relative to the viral spike protein. The center of mass of the $\alpha$-carbons of all residues (163-318 in linear numbering) in GP1 received an applied force during the simulation. The NAMD convention does not actually apply a force to all $\alpha$-carbon atoms, but rather uses the selection to compute an initial center of mass. Then, during the steering run, the single center of mass point is pulled with the parameters desribed below. We used the same force field parameters (exclude, cutoff, switching, etc.), the same integrator parameters (time step, rigidbonds on, all molecular being wrapped, etc.), and the same particle mesh ewald parameters as in equilibration. Periodic boundary conditions were incorporated as part of the system (as is the convention in NAMD restart) and PME was again used to approximate full system electrostatics.

We ran test simulations at several force constants and visually inspected the results. A force constant of 5~kcal/mol/\AA$^2$ was chosen due to its relatively low signal-to-noise ratio. This constant is slightly lower than the more common 7~kcal/mol/\AA$^2$ found in several recent studies; that value is commonly selected primarily because it is the force constant found in the NAMD, SMD tutorial available through the developers. Moreover, the force constant could very likely be set to a range of nearby values with little loss in predictive power. In SMD experiments the pulling velocity should be as low as possible for the available computational time \citet{Cuendet2008,Cuendet2011}. Thus we choose a velocity of 0.000001~\AA/fs = 1~\AA/ns, and direction down the positive $z$-axis. This number could be set to pull faster if the computing time must be reduced, but slower than necessary pulling speeds are not typically considered problematic.

@@

Again, the NAMD configuration file is made available via github. We used a similar configuration to that in equilibration. One significant difference was to make a cubic water box with a side length equal to the long axis of the complex plus a 10~\AA\  buffer on either side, and simply restrict center of mass motion with the NAMD setting. This was done to avoid affecting the system energy while calculating free energy differences.

@@

The FEP analysis tool in VMD was used for subsequent analysis. We used it to perform error analysis and compute the Bennett acceptance ratio as the maximum likelihood free energy difference of the two states under consideration. Though the larger transitions presented difficulty in a small number of windows, forward and reverse hysteresis was generally in good agreement for all complexes. The double mutants were performed by first doing the Y211A mutation followed by the other of the two mutants. Then, the $\Delta G$'s were simply added together to get the total energetic difference.

@@

\subsection{The GP1/hTfR1 system}
The GP1/hTfR1 interface marks a particularly important and useful test system. There are several sites on both the human and viral protein known to affect the infectivity phenotype of MACV. Many of the important sites have been mapped by \textit{in vitro} flow-cytometry based entry assays. The GP1/hTfR1 interface appears not to be dominated by one particular type of interaction (electrostatics, hydrogen-bonding, or van der Waals). In addition, much of the binding domain on hTfR1 is on a loop that is flexible prior to viral binding, but organizes to become a strand of a $\beta$-sheet on binding. As a result,  many other computational techniques \citep{Grant2011,Kortemme2004} are only marginally useful. The complex nature of this interface represents a particularly difficult challenge for traditional computational analysis.

In total, we tested 7 point mutants and 3 double mutants in addition to the WT complex (Table~\ref{tab:summary_mutants} and Figure~\ref{fig:mutant_comparison}). All of the mutations are within 5~\AA\ of the protein--protein interface. Mutations in hTfR1 at site 211 have proven capable of causing loss-of-entry according to \textit{in vitro} flow-cytometry infection assays or known host-range limitations \citep{Rad2008,Rad20111,Rad20112}. Most likely, this effect is caused by the destruction of a critical hydrogen bond to Ser113 or Ser111 in GP1. The lost hydrogen bond would lead to the subsequent loss of a large hydrogen-bonding network seen in the crystal structure (Table~\ref{tab:summary_mutants}) \citep{Abraham2010}. In a manner similar to site 211, Asn348 appears to be important for binding by participating in a critical hydrogen bonding network \citep{Rad2008,Abraham2010} to GP1. In particular, Asn348Lys is reported in the literature to cause significantly reduced viral entry \textit{in vivo} (Table~\ref{tab:summary_mutants}) \citep{Rad2008,Abraham2010}. Finally, an alanine mutation at site 111 in GP1 (mutation vArg111Ala) has also been shown to cause decreased entry (Table~\ref{tab:summary_mutants}) \citep{Rad20112}. For notation purposes, the viral site is always referred to with a preceding `v'.

Despite the fact that viral binding occurs at the site of a flexible loop in the free hTfR structure, our data shows after binding the strand is extremely rigid. In the bound conformation, two sites of the loop have root mean squared fluctuation (RMSF) values in the top half of all receptor sites during equilibration (Figure~\ref{fig:rmsf}), and those are almost completely exposed to solvent. This is unsurprising considering the high degree of burial that occurs as a result of viral binding. Computing the root mean squared deviation (RMSD) of the entire structure over the trajectory shows that none of the mutations are so deleterious as to cause rapid unbinding. In fact, the RMSD over trajectory looks highly invariant across mutants (Figure~\ref{fig:rmsd}). By comparison to the equilibration RMSF calculation, near the end of the SMD trajectory all of the residues in the WT receptor interfacial strand are in the top half of RMSF over all receptor sites (Figure~\ref{fig:rmsf_comparison}). Thus, if sufficient simulation time is not dedicated to allowing this unfolding process, standard free energy techniques may miss the energetic contributions that result from ordering the flexible loop in the hTfR apical domain.

@@

We proceeded to compare our SMD results to that of the standard dual topology FEP approach to calculate relative free energy differences. The correlation between the energetically rigorous FEP and our statistical approach is high. For all 11 complexes tested, the correlation between max force and FEP was $r=-0.767$ at $p=0.005857$ (Figure~\ref{fig:fep}), and the correlation between AUC and FEP was $r=--0.729$ at $p=0.011$. Because of this strong correlation, we refer exclusively to the SMD results for the remainder of this work.

@@

We would like to emphasize here that we cannot expect perfect agreement between our simulations and the available experimental data, but the correspondence to a well established free energy method bolsters our conclusions. While we have shown that our method can distinguish individual point mutations, we do not know the limit of detection with our method. First, it is possible that some mutants display measurable phenotypic effects in experiments yet appear identical in simulation. More extensive sampling or refinement of the simulation protocol could help to differentiate such mutants (see also next paragraph). Second, the SMD method is fundamentally limited by the accuracy of our starting structure. Third, the available experimental data for the GP1/hTfR1 system were generally obtained from entry assays or whole-cell binding assays rather than molecular binding assays. A mutant may cause a phenotypic difference in infectivity without generating a signal by our method. For example, entry could be lost in the experimental system because the protein is grossly or partially misfolded. An additional analytical step with circular dichroism or an analogous technique could clarify such large-scale folding differences. Further, since our simulations start with a bound structure, any changes that may dramatically affect the rate of association (different folds, trafficking issues, etc.) or relative orientation of the two proteins would be underestimated by our method.

@@

More importantly, with no \textit{a priori} knowledge of the appropriate number of equilibration samples, the best duration of equilibration, the appropriate number of pulling runs, or the best pulling speed means the computational expense in our SMD protocol may not be commensurate with the information provided. For example, another all atom approach that makes calculations via short simulations of spatially restrained complexes has proven capable of generating relatively accurate binding affinities with less compute time than is required from our steering strategy \citep{Gumbart2013,Gumbart2013b}. That being said, there is no reason to believe this SMD approach to mutagenic studies could not be optimized to reduce computational expense. Further analysis would be needed to understand the lower limits of resources required for accurate predictions.

@@

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/rmsfs.pdf}}
\caption{\label{fig:rmsf}\title{RMSF values during equilibration.} The RMSF values for every site in the bound complex computed during the equilibration phase of the protocol. Each color represents the average over 20 trajectories of a single mutant. Indices 17-25 are the hTfR flexible loop. The plot shows the flexibility of each site is essentially independent of mutation, and two sites (indices 17 and 18) above 0.72~\AA\ are a part of the flexible loop in the free receptor. However, these two residues are not actually found in the protein--protein interface, but rather are almost completely solvent exposed with the virus bound.}
\end{figure}

@@

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/fep_mutants.pdf}}
\caption{\label{fig:fep}\title{Max force versus free energy perturbation.} Scatter plot of maximum force in SMD versus the relative free energy difference calculated by FEP for all 10 mutants tested plus the WT complex. The WT complex for FEP was simply set to 0.0. The correlation between the two is $r=-0.767$ with $p=0.005857$.}
\end{figure}
